Tunnels to Towers: Secure Virtual Private Networking for CCN

### 2017-01-11 paper/05-sec-analysis.tex
better plot ins experiments section

\section{Security Analysis}\label{sec:sec-analysis}
 TODO

>>>>

\section{Security Analysis}\label{sec:sec-analysis}

\todo{TODO: Introductory text about the sec analysis}

\begin{definition}
\textit{
An interest encapsulation algorithm $Encapsulate(I_p)$ is an indistinguishable interest encapsulation iff, given any two interests $I_p^1$ and $I_p^2$, chosen by the adversary, and a randomly selected bit $b$, the adversary has only $1/2 + \epsilon$ probability of guessing the value of the bit $b$ when given $I_e^b = Encapsulate(I_p^b)$. Where $\epsilon$ is a negligible factor with regard to the security parameter $k$.
}
\end{definition}

\begin{theorem}
\textit{
Let $Encapsulate_{pk}(I_p)$ denote the interest encapsulation routine described in Algorithm~\ref{alg:interestEncap}. If $Enc_{pk}$, used to construct $Encapsulate_{pk}(I_p)$, is a CPA-secure public-key encryption scheme then $Encapsulate_{pk}(I_p)$ is an indistinguishable interest encapsulation algorithm.
}
\end{theorem}

\textit{\textbf{Proof--}}
\todo{TODO}

\begin{definition}
\textit{
A content encapsulation algorithm $Encapsulate(C_p)$ is an indistinguishable content encapsulation iff, given any two contents $C_p^1$ and $C_p^2$, chosen by the adversary, and a randomly selected bit $b$, the adversary has only $1/2 + \epsilon$ probability of guessing the value of the bit $b$ when given $C_e^b = Encapsulate(C_p^b)$. Where $\epsilon$ is a negligible factor with regard to the security parameter $k$.
}
\end{definition}

\begin{theorem}
\textit{
Let $ContentEnc_{k_r}(C_p)$ denote the content encapsulation routine described in Algorithm~\ref{alg:contentEnc}. If $EncryptThenMAC_{k_r}$, used to construct $ContentEnc_{sk}$, is a CCA-secure symmetric-key encryption scheme, then:
\begin{enumerate}
\item $ContentEnc_{k_r}(C_p)$ is an indistinguishable content encapsulation algorithm;
\item An adversary has only negligible probability of generating a valid fake encapsulated content $I_c'$
\end{enumerate}
}
\end{theorem}

\textbf{\textit{Proof--}}
\todo{TODO}

### 2017-01-11 paper/07-experiment.tex
first draft of sec analysis section (5)
sec:analysis
better plot ins experiments section

@@

\begin{figure*}[!t]
\centering
  \subfigure[1 Consumer x 1 Producer]{\includegraphics[width=1.5in]{throughput_pk_1_1.png}\label{1a}}
  \hfil
  \subfigure[2 Consumers x 1 Producer]{\includegraphics[width=1.5in]{throughput_pk_2_1.png}\label{1b}}
  \hfil
  \subfigure[3 Consumers x 1 Producer]{\includegraphics[width=1.5in]{throughput_pk_3_1.png}\label{1c}}
  \hfil
  \subfigure[4 Consumers x 1 Producer]{\includegraphics[width=1.5in]{throughput_pk_4_1.png}\label{1d}}
\caption{Throughput per consumer in public key mode. 1 Producer N consumers}\label{exp1}
\end{figure*}

\begin{figure*}[!t]
\centering
  \subfigure[1 Consumer x 1 Producer]{\includegraphics[width=1.5in]{throughput_pk_1_1.png}\label{2a}}
  \hfil
  \subfigure[2 Consumers x 2 Producers]{\includegraphics[width=1.5in]{throughput_pk_2_2.png}\label{2b}}
  \hfil
  \subfigure[3 Consumers x 3 Producers]{\includegraphics[width=1.5in]{throughput_pk_3_3.png}\label{2c}}
  \hfil
  \subfigure[4 Consumers x 4 Producers]{\includegraphics[width=1.5in]{throughput_pk_4_4.png}\label{2d}}
\caption{Throughput per consumer in public key mode. N Producers N consumers}\label{exp2}
\end{figure*}

\begin{figure*}[!t]
\centering
  \subfigure[1 Consumer x 1 Producer]{\includegraphics[width=1.5in]{throughput_sk_1_1.png}\label{3a}}
  \hfil
  \subfigure[2 Consumers x 1 Producer]{\includegraphics[width=1.5in]{throughput_sk_2_1.png}\label{3b}}
  \hfil
  \subfigure[3 Consumers x 1 Producer]{\includegraphics[width=1.5in]{throughput_sk_3_1.png}\label{3c}}
  \hfil
  \subfigure[4 Consumers x 1 Producer]{\includegraphics[width=1.5in]{throughput_sk_4_1.png}\label{3d}}
\caption{Throughput per consumer in symmetric key mode. 1 Producer N consumers}\label{exp3}
\end{figure*}

\begin{figure*}[!t]
\centering
  \subfigure[1 Consumer x 1 Producer]{\includegraphics[width=1.5in]{throughput_sk_1_1.png}\label{4a}}
  \hfil
  \subfigure[2 Consumers x 2 Producers]{\includegraphics[width=1.5in]{throughput_sk_2_1.png}\label{4b}}
  \hfil
  \subfigure[3 Consumers x 3 Producers]{\includegraphics[width=1.5in]{throughput_sk_3_1.png}\label{4c}}
  \hfil
  \subfigure[4 Consumers x 4 Producers]{\includegraphics[width=1.5in]{throughput_sk_4_1.png}\label{4d}}
\caption{Throughput per consumer in symmetric key mode. N Producers N consumers}\label{exp4}
\end{figure*}

>>>>

\todo{TODO: Add results discussion}

@@

\begin{figure}[!t]
\centering
  \subfigure[1 Consumer x 1 Producer]{\includegraphics[width=1.5in]{images/throughput_1_1.png}\label{1a}}
  \hfil
  \subfigure[2 Consumers x 1 Producer]{\includegraphics[width=1.5in]{images/throughput_2_1.png}\label{1b}}
  \hfil
  \subfigure[3 Consumers x 1 Producer]{\includegraphics[width=1.5in]{images/throughput_3_1.png}\label{1c}}
  \hfil
  \subfigure[4 Consumers x 1 Producer]{\includegraphics[width=1.5in]{images/throughput_4_1.png}\label{1d}}
\caption{Throughput per consumer. 1 Producer X N consumers}\label{exp1}
\end{figure}

\begin{figure}[!t]
\centering
  \subfigure[1 Consumer x 1 Producer]{\includegraphics[width=1.5in]{images/throughput_1_1.png}\label{4a}}
  \hfil
  \subfigure[2 Consumers x 2 Producers]{\includegraphics[width=1.5in]{images/throughput_2_2.png}\label{4b}}
  \hfil
  \subfigure[3 Consumers x 3 Producers]{\includegraphics[width=1.5in]{images/throughput_3_3.png}\label{4c}}
  \hfil
  \subfigure[4 Consumers x 4 Producers]{\includegraphics[width=1.5in]{images/throughput_4_4.png}\label{4d}}
\caption{Throughput per consumer. N Producers X N consumers}\label{exp4}
\end{figure}
